Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-08-10 ltx/data_paper/DataPaper.tex
edits to results discussion and the conclusion

substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:EM-Stateequationnonlinearity},  an approximation for $\mathbf q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ can be obtained

@@

$\mathbf q(\mathbf{x}_t)$&\eqref{eq:EM-Stateequationnonlinearity}&$O(n_xn_{\theta}n_r)$\\

>>>>

substituting \eqref{eq:SigmoidTaylor} in \eqref{eq:QmatrixForSigmapoints},  an approximation for $\mathbf q(\mathbf x_t)$ around the smoothed state $\hat{\mathbf{x}}_t^b$ can be obtained

@@

$\mathbf q(\mathbf{x}_t)$&\eqref{eq:QmatrixForSigmapoints}&$O(n_xn_{\theta}n_r)$\\
